### 2017-11-04 submission/manuscript.Rmd
add study n tables

@@

**Table 1:**

@@

studies <- c("Ahn", "Baxter", "Brim", "Burns", "Chen", "Dejea", "Flemer", "Geng", "Hale", "Lu", "Sanapareddy", "Wang", "Weir", "Zeller")

@@

>>>>

#Read study data files
stool_n <- read_csv("../data/process/tables/stool_study_n_analyzed.csv")
tissue_n <- read_csv("../data/process/tables/tissue_study_n_analyzed.csv")

@@

**Table 1: Studies with Stool Samples Included in the Analysis**

\footnotesize

@@

stool_n <- stool_n %>% arrange(study)

studies <- c("Ahn", "Baxter", "Brim", "Flemer", "Hale", "Wang", "Weir", "Zeller")

data_obtained <- c("DBGap", "SRA", "SRA", "Author", "Author", "SRA", "Author", "SRA")

variable_region <- c("V3-4", "V4", "V1-3", "V3-4", "V3-5", "V3", "V4", "V4")

con_n <- gsub("NA", 0, str_replace_na(stool_n$control))
adn_n <- gsub("NA", 0, str_replace_na(stool_n$adenoma))
crc_n <- gsub("NA", 0, str_replace_na(stool_n$cancer))

table1 <- cbind(studies, data_obtained, variable_region, con_n, adn_n, crc_n)

colnames(table1) <- c("Study", "Data Stored", "16S Region", "Controls", "Adenoma", "Carcinoma")

@@

\normalsize
\newpage

**Table 2: Studies with Tissue Samples Included in the Analysis**

\footnotesize

```{r table2, echo=FALSE, message=FALSE, warning=FALSE}

tissue_n <- tissue_n %>% arrange(study)

studies <- c("Burns", "Chen", "Dejea", "Flemer", "Geng", "Lu", "Sanapareddy")

data_obtained <- c("SRA", "SRA", "SRA", "Author", "SRA", "SRA", "Author")

variable_region <- c("V5-6", "V1-V3", "V3-5", "V3-4", "V1-2", "V3-4", "V1-2")

con_n <- tissue_n$control
adn_n <- gsub("NA", 0, str_replace_na(tissue_n$adenoma))
crc_n <- gsub("NA", 0, str_replace_na(tissue_n$cancer))

table2 <- cbind(studies, data_obtained, variable_region, con_n, adn_n, crc_n)

colnames(table2) <- c("Study", "Data Stored", "16S Region", "Controls", "Adenoma", "Carcinoma")

kable(table2, format = "markdown", align = 'c', padding = 2)
```

\normalsize
\newpage

### 2017-11-04 submission/manuscript.tex
add study n tables

\textbf{Results.} There was a significant decrease from control to
adenoma to carcinoma for both Shannon diversity and evenness for fecal
samples (P-value \textless{} 0.05) after correcting for study and
variable region. Lower Shannon diversity and evennes in fecal samples
resulted in a significant increase in relative risk for carinoma
(P-value \textless{} 0.05) but not adenoma (P-value \textgreater{}
0.05). Previously associated colorectal cancer genera
(\emph{Fusobacterium}, \emph{Parvimonas}, \emph{Peptostreptococcus}, or
\emph{Porphyromonas}) followed a similar pattern with a significantly
increased relative risk by their presence for carcinoma (P-value
\textless{} 0.05) but not adenoma (P-value \textgreater{} 0.05) with the
exception of \emph{Porphyromonas} (P-value \textless{} 0.05). Using the
whole community resulted in a higher classification model AUC for both
adenoma and carcinoma for fecal and tissue samples. Most studies are
adequately powered for large effect size differences which may be more
amenable for carcinoma than for adenoma.

@@

\textbf{Table 1:}

\begin{longtable}[]{@{}cccc@{}}
\toprule
country & year & cases & population\tabularnewline
\midrule
\endhead
Afghanistan & 1999 & 745 & 19987071\tabularnewline
Afghanistan & 2000 & 2666 & 20595360\tabularnewline
Brazil & 1999 & 37737 & 172006362\tabularnewline
Brazil & 2000 & 80488 & 174504898\tabularnewline
China & 1999 & 212258 & 1272915272\tabularnewline
China & 2000 & 213766 & 1280428583\tabularnewline
\bottomrule
\end{longtable}

>>>>

\textbf{Results.} There was a significant decrease from control to
adenoma to carcinoma for both Shannon diversity and evenness for fecal
samples (P-value \textless{} 0.05) after correcting for study and
variable region. Lower Shannon diversity and evennes in fecal samples
resulted in a significant increase in relative risk for carinoma
(P-value \textless{} 0.05) but not adenoma (P-value check tables 0.05).
Previously associated colorectal cancer genera (\emph{Fusobacterium},
\emph{Parvimonas}, \emph{Peptostreptococcus}, or \emph{Porphyromonas})
followed a similar pattern with a significantly increased relative risk
by their presence for carcinoma (P-value \textless{} 0.05) but not
adenoma (P-value \textgreater{} 0.05) with the exception of
\emph{Porphyromonas} (P-value \textless{} 0.05). Using the whole
community resulted in a higher classification model AUC for both adenoma
and carcinoma for fecal and tissue samples. Most studies are adequately
powered for large effect size differences which may be more amenable for
carcinoma than for adenoma.

@@

\textbf{Table 1: Studies with Stool Samples Included in the Analysis}

\footnotesize

\begin{longtable}[]{@{}cccccc@{}}
\toprule
Study & Data Stored & 16S Region & Controls & Adenoma &
Carcinoma\tabularnewline
\midrule
\endhead
Ahn & DBGap & V3-4 & 148 & 0 & 62\tabularnewline
Baxter & SRA & V4 & 172 & 198 & 120\tabularnewline
Brim & SRA & V1-3 & 6 & 6 & 0\tabularnewline
Flemer & Author & V3-4 & 37 & 0 & 43\tabularnewline
Hale & Author & V3-5 & 473 & 214 & 17\tabularnewline
Wang & SRA & V3 & 56 & 0 & 46\tabularnewline
Weir & Author & V4 & 4 & 0 & 7\tabularnewline
Zeller & SRA & V4 & 50 & 37 & 41\tabularnewline
\bottomrule
\end{longtable}

\normalsize
\newpage

\textbf{Table 2: Studies with Tissue Samples Included in the Analysis}

\footnotesize

\begin{longtable}[]{@{}cccccc@{}}
\toprule
Study & Data Stored & 16S Region & Controls & Adenoma &
Carcinoma\tabularnewline
\midrule
\endhead
Burns & SRA & V5-6 & 18 & 0 & 16\tabularnewline
Chen & SRA & V1-V3 & 9 & 0 & 9\tabularnewline
Dejea & SRA & V3-5 & 31 & 0 & 32\tabularnewline
Flemer & Author & V3-4 & 103 & 37 & 94\tabularnewline
Geng & SRA & V1-2 & 16 & 0 & 16\tabularnewline
Lu & SRA & V3-4 & 20 & 20 & 0\tabularnewline
Sanapareddy & Author & V1-2 & 38 & 0 & 33\tabularnewline
\bottomrule
\end{longtable}

\normalsize
\newpage
